Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-18 awipev-CO2.Rmd
Corrected crontab information

* (Every hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
* (Every hour at 10 min past the hour, the web page is generated)
    + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 
* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

>>>>

* (Every 4 hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
* (Every 4 hour at 10 min past the hour, the web page is generated)
    + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 
* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
